\begin{thebibliography}{10}

\bibitem{g1} Peter Likarish, Eunjin (EJ) Jung, Chris Boyce. {\it Towards a Robust Detection of Malicious JavaScript(TARDIS)}, Unpublished paper

\bibitem{g2} The Open Web Application Security Project(OWASP). The owasp top ten project.
{\small\verb+https://www.owasp.org/index.php/Category: OWASP_Top_Ten_Project./+}

\bibitem{g3} Peter Likarish, Eunjin (EJ) Jung, Insoon Jo. Obfuscated Malicious JavaScript Detection using Classification Techniques, {\it  second edition, Prentice Hall,}  1991.

\bibitem{g4} Pavel Laskov and Nedim Srndic. Static Detection of Malicious-JavaScript-bearing PDF Documents. {\it In Proceedings of the 27th Annual Computer Security Applications Conference. }ACM, 2011.

\bibitem{g5} Same-origin policy. Web. Retrieved December 2015, from\\
{\small\verb+https://developer.mozilla.org/en- US/docs/Web/Security/Same-origin_policy+}

\bibitem{g6} Wei Xu, Fangfang Zhang, Scencum Zhu. JStill: Mostly Static Detection of Obfuscated
Malicious JavaScript Code. {\it In Proceedings of the third ACM conference on Data and
application security and privacy. ACM, 2013.}

\bibitem{g7} Mario Heiderich, Tilman Frosch and Thorsten Holz. IceShield: Detection and Mitigation of Malicious Websites with a Frozen DOM. {\it Recent Advances in Intrusion Detection Volume 6961 of the series Lecture Notes in Computer Science.} pp 281-300.

\bibitem{g8} Phu H.~ Phung, Lieven Desmet. A Two-tier sandbox architecture for untrusted JavaScript. {\it In Proceedings of the Workshop on JavaScript Tools.} Pages 1-10. ACM, 2012.

\bibitem{g9} Fergal Glynn. JavaScript Security. Web. Retrieved March 2015, from\\
{\small\verb+http://www.veracode.com/security/javascript-security+}

\bibitem{g10} Kevin Whinnnery. Comparing Titanium and PhoneGap. (May 12, 2012). Web. Retrieved March 2015, from\\
 {\small\verb+http://www.appcelerator.com/blog/2012/05/comparing-titanium-and-phonegap/+}

\bibitem{g11} What is Statistical Language Modeling. Web. Retrieved April 2015, from\\
 {\small\verb+http://homepages.inf.ed.ac.uk/lzhang10/slm.html+}

\bibitem{g12} Cross Site Scripting.  Retrieved April 2015, Web. Retrieved March 2015, from\\ 
 {\small\verb+https://www.owasp.org/index.php/Cross-site_Scripting_(XSS)+}

\bibitem{g13} Non- Persistent cross site scripting. Web. Retrieved April 2015, from\\
 {\small\verb+http://www.acunetix.com/blog/articles/non-persistent-xss/+}

\bibitem{g14} Client-Side Attacks. Web. Retrieved April 2015, from\\
 {\small\verb+ http://neokobo.blogspot.com/2014/01/3218-client-side-attacks.html+}

\bibitem{g15} Chuan Yue, Haining Wang. Characterizing Insecure JavaScript Practices on the Web. {\it In proceedings of the 18th international conference on World wide web.} pages 961-970. ACM 2009. 

\bibitem{g16} Davide Canali, Marco Cova, Giovanni Vigna, Christopher Kruegel. Prophiler: A Fast Filter for the Large-Scale Detection of Malicious Web Pages. {\it In proceedings of the 20th international conference on World wide web.} pages 197-206. ACM 2011 

\bibitem{g17} Obfuscation of client side JavaScript. Web. Retrieved April 2015, from\\  
 {\small\verb+ http://stunnix.com/prod/jo/sample.shtml+}

\bibitem{g18} Firefox Add-ons SDK. Web. Retrieved April 2015, from\\
 {\small\verb+ https://developer.mozilla.org/en-US/Add-ons+}

\bibitem{g19} Cross-Site Request Forgery (CSRF). Web. Retrieved April 2015, from\\
 {\small\verb+https://www.owasp.org/index.php/Cross-Site_Request_Forgery_(CSRF)+}

\bibitem{g20} DOM-based Cross-Site Scripting(XSS) explained. Web. Retrieved April 2015, from\\
 {\small\verb+http://www.acunetix.com/blog/articles/dom-xss-explained/+}

\bibitem{g21} ChengXiang Zhai. Statistical Language Models for Information Retrieval A Critical Review. Web. Retrieved March 2016. From\\
  {\small\verb+http://sifaka.cs.uiuc.edu/czhai/pub/slmir-now.pdf+}

\bibitem{g22} M.~Stamp, {\it Information Security: Principles and Practice}, second edition, 
Wiley, 2011

\bibitem{g23} Konrad Rieck, Tammo Krueger, Andreas Dewald. Cujo: Efficient Detection and Prevention of Drive-by-Download Attacks. {\it In Proceedings of the 26th Annual Computer Security Applications Conference.} Pages 31-39. ACM, 2010

\bibitem{g24} Charlie Curtsinger, Benjamin Livshits, Benjamin Zorn, Christian Seifert. ZOZZLE: Fast and Precise In-Browser JavaScript Malware Detection. {\it In Proceedings of the 20th USENIX conference on Security.} Pages 3-3. USENIX Association 2011
\bibitem{g25} Kristof Schutt, Marius Kloft, Alexander Bikadorov, Konrad Rieck. Early Detection of Malicious Behavior in JavaScript Code. {\it In Proceedings of the 5th ACM workshop on Security and artificial intelligence.} Pages 15-24. ACM, 2012

\end{thebibliography}
